---
title: "introvrt"
author: "Anmol Gairola"
date: "12/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

data = read.csv("introvert.csv")
head(data)

```

```{r}

library(tidyverse)
library(ggplot2)

violet = "#9f61b8"
indigo = "#6761b8"
blue = "#61b8a2"
green = '#7ab861'
yellow = "#b8ae61"
orange = "#b88861"
red = "#b86161"
```

```{r}

dataIntro = data %>% 
  filter(IE == 1)

head(dataIntro)

dataExtro = data %>% 
  filter(IE == 2)

```

```{r}

dataExtroWomen = dataExtro %>% 
  filter(gender == 2)

dataIntroWomen = dataIntro %>% 
  filter(gender == 2)

dataExtroMen = dataExtro %>% 
  filter(gender == 1)

dataIntroMen = dataIntro %>% 
  filter(gender == 1)

```

Interesting questions to explore

 "Q3" : "I have to psych myself up before I am brave enough to make a phone call."
 
"Q7" : "I spend hours alone with my hobbies."
  
"Q8" : "I prefer to eat alone."

"Q9" : "I have trouble finding people I want to be friends with."

"Q10" : "I prefer to socialize 1 on 1, than with a group."

"Q22" : "I naturally emerge as a leader."
 
"Q32" : "I would like to try bungee jumping."
 
"Q33" : "I tend to be admired by others."
  
"Q52" : "I am hesitant to give suggestions." 
 
"Q59" : "I hate to ask for help."

"Q77" : "I am happy with my life."

```{r}
#"Q3" : "I have to psych myself up before I am brave enough to make a phone call."

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q3A), fill = red) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")


ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q3A), fill = indigo) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```



```{r}
#"Q7" : "I spend hours alone with my hobbies."

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q7A), fill = green) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")


ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q7A), fill = blue) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```

```{r}
#"Q8" : "I prefer to eat alone."

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q8A), fill = yellow) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")


ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q8A), fill = orange) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```

```{r}
#"Q9" : "I have trouble finding people I want to be friends with."

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q9A), fill = red) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")


ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q9A), fill = green) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```

```{r}
#"Q10" : "I prefer to socialize 1 on 1, than with a group."

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q10A), fill = blue) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")


ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q10A), fill = yellow) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```

```{r}
#"Q22" : "I naturally emerge as a leader."

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q22A), fill = orange) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")


ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q22A), fill = green) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```

```{r}
#Q32" : "I would like to try bungee jumping."

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q32A), fill = yellow) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")


ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q32A), fill = blue) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```

```{r}
#Q52" : "I am hesitant to give suggestions." 

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q52A), fill = green) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")

ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q52A), fill = red) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```

```{r}
#"Q59" : "I hate to ask for help."

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q59A), fill = indigo) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")


ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q59A), fill = orange) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```

```{r}
#"Q77" : "I am happy with my life."

ggplot(data = dataIntro) + 
  geom_bar(mapping = aes(x=Q77A), fill = green) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Introverts")


ggplot(data = dataExtro) + 
  geom_bar(mapping = aes(x=Q77A), fill = blue) + 
  scale_x_discrete(name ="Responses", limits=c("Disagree","Slightly Dsiagree","Neutral", "Slightly Agree", "Agree"))+
  ylab("Count")+
  ggtitle("Extroverts")

```
